Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/paper.tex
extensions removal
draft compilation in comment
some small fixes

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\urlstyle{rm}

@@

    \section{Introduction}
    \input{introduction.tex}

@@

    \section{Visibility through tangency of chords}
    \input{visibility.tex}

@@

    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
    elements of the 2 lists. If they don't overlap (i.e. the start and end of the 1st interval are both smaller than
    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
    is empty returns the intersection of both lists of intervals.

@@

    \paragraph{Saliency-aware normal estimator.}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some
    $\Theta(\sqrt{h})$), then this estimator is observed to be
    multigrid convergent along digitization of smooth shapes. However,
    since the computation window is limited by the visibility, it
    better approximates the geometry near sharp or salient features.

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
                \raisebox{18mm}{$\kappa_1$} &
                \MyZoom{pictures/d20-k1-II.jpg} &
                \MyZoom{pictures/d20-k1-CTriv.jpg}&
                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
                \raisebox{18mm}{$\kappa_2$} &
                \MyZoom{pictures/d20-k2-II.jpg} &
                \MyZoom{pictures/d20-k2-CTriv.jpg}&
                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
                \raisebox{18mm}{$H$} &
                \MyZoom{pictures/d20-H-II.jpg} &
                \MyZoom{pictures/d20-H-CTriv.jpg}&
                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
                \raisebox{18mm}{$G$} &
                \MyZoom{pictures/d20-G-II.jpg} &
                \MyZoom{pictures/d20-G-CTriv.jpg}&
                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
            \end{tabular}
        \end{center}
        \caption{\label{fig-curvatures}Estimation of curvatures using
          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
          with a measure of radius $2$ for the shape ``Dice-20'' of
          Thingi10K database at resolution $256^3$. This estimator is
          parameterized by an input normal estimator: first column by
          ``Integral Invariant normals'' (radius $r=6$), second column
          by ``Convolved Trivial normals'' (radius $k=6$), third
          column by our presented normal estimator (deviation
          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
          estimated curvatures in order: first and second principal
          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
          Gaussian curvature $G$. The range of curvature between deep
          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
          color equal to $0$.}
    \end{figure}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%\documentclass[draft]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\urlstyle{rm}

@@

    \section{Introduction}
    \input{introduction}

@@

    \section{Visibility through tangency of chords}
    \input{visibility}

@@

    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
    elements of the 2 lists. If they don't overlap (i.e.\ the start and end of the 1st interval are both smaller than
    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
    is empty returns the intersection of both lists of intervals.

@@

    \paragraph{Saliency-aware normal estimator.}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some
    $\Theta\left(\sqrt{h}\right)$), then this estimator is observed to be
    multigrid convergent along digitization of smooth shapes. However,
    since the computation window is limited by the visibility, it
    better approximates the geometry near sharp or salient features.

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
                \raisebox{18mm}{$\kappa_1$} &
                \MyZoom{pictures/d20-k1-II.jpg} &
                \MyZoom{pictures/d20-k1-CTriv.jpg}&
                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
                \raisebox{18mm}{$\kappa_2$} &
                \MyZoom{pictures/d20-k2-II.jpg} &
                \MyZoom{pictures/d20-k2-CTriv.jpg}&
                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
                \raisebox{18mm}{$H$} &
                \MyZoom{pictures/d20-H-II.jpg} &
                \MyZoom{pictures/d20-H-CTriv.jpg}&
                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
                \raisebox{18mm}{$G$} &
                \MyZoom{pictures/d20-G-II.jpg} &
                \MyZoom{pictures/d20-G-CTriv.jpg}&
                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
            \end{tabular}
        \end{center}
        \caption{\label{fig:fig-curvatures}Estimation of curvatures using
          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
          with a measure of radius $2$ for the shape ``Dice-20'' of
          Thingi10K database at resolution $256^3$. This estimator is
          parameterized by an input normal estimator: first column by
          ``Integral Invariant normals'' (radius $r=6$), second column
          by ``Convolved Trivial normals'' (radius $k=6$), third
          column by our presented normal estimator (deviation
          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
          estimated curvatures in order: first and second principal
          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
          Gaussian curvature $G$. The range of curvature between deep
          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
          color equal to $0$.}
    \end{figure}
